---
title: "preprocessing"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'h', 
  echo = FALSE,    # Hide code by default
  warning = FALSE, # Hide warnings by default
  message = FALSE, # Hide messages by default
  error = FALSE    # Hide errors by default
)
```

Note to self 21.01.24. you want to load in all data without grouping (so including quest data, but not grouping of survey data so that you can exclude participants from calculations in the analysis script)

# libraries
```{r, echo=T, message=FALSE, warning=FALSE}
# let's load in the libraries we need for the following session. 
library(tidyverse)
library(readxl) 
library(stringr)
```

# load experiment data
note: for map_df() to work this markdown must be placed within the actual data folder. i.e. it has to be here: "..\data"
```{r, echo=T, message=FALSE, warning=FALSE}
pm_import <-
    list.files(pattern = "n49w|eu79|tfo5|3k5q", recursive = T) %>% #search all files in all directories contain the string in pattern
    map_df(~read_csv(., col_types = cols(.default = "c"))) #return data frames by row- or column-binding the outputs together.
```

# preprocessing
check import
select columns/rename 

## check import

```{r, warning = F, message=F}
# check for number of versions and observations in. 
pm_import$'Experiment ID' <- factor(pm_import$'Experiment ID') 
levels(pm_import$'Experiment ID')
summary(pm_import$'Experiment ID')
#142915 is nsl with high quality images, 146116 low quality, and 142915 is rsl, nas are white spaces between file concatenation
```

## choose columns/rename
```{r, warning = F, message=F}
pm_selected <-
  pm_import %>%
  dplyr::select(
    "Participant Private ID",
    "Response Type",
    "Response",
    "Spreadsheet: display",
    "Spreadsheet: picture",
    "Spreadsheet: condition",
    "Trial Number", 
    "Spreadsheet",
    "Spreadsheet: item",
    "Spreadsheet: trial",
    "Reaction Time") %>% 
  rename(
    "id"= "Participant Private ID",
    "type" = "Response Type",
    "response" = "Response",
    "target"= "Spreadsheet: display",
    "pic_id" = "Spreadsheet: picture",
    "oops" ="Spreadsheet: condition",
    "trial" = "Trial Number",
    "list" = "Spreadsheet",
    "item" = "Spreadsheet: item",
    "trial_type" = "Spreadsheet: trial",
    "raw_rt" = "Reaction Time")
```

## filter

```{r, warning = F, message=F}
# parse out only the rows we need (response is key-presses to items, target is not the foils)
distinct(pm_selected, type)
distinct(pm_selected, trial_type)
distinct(pm_selected, response)
distinct(pm_selected, target)
distinct(pm_selected, pic_id)
distinct(pm_selected, oops)

pm_subset <-
  pm_selected %>%
  filter(type == "response", #only responses to trials gorilla
         trial_type == "target") #only experimental trials
```

## list check 
check number of participants per list
```{r, warning = F, message=F}
#participants per list
pm_subset %>%
    group_by(list) %>% 
    summarize(count = n_distinct(id))

```

# control response vars
Accuracy was not calculated in Gorilla, but is instead determined here.

## accuracy calc
if response (match/nomatch) = target (match/nomatch) then correct (1), if not incorrect (0)
```{r}
distinct(pm_selected, response)
distinct(pm_selected, target)

pm_subset_accuracy <- pm_subset %>% mutate(correct = if_else(response == target, 1, 0))
# View(pm_subset_accuracy)
item_accuracy <- pm_subset_accuracy %>%
  group_by(item) %>%
  summarise(mean_acc = mean(correct)) %>% 
  arrange(mean_acc)
item_accuracy #global
 
participant_accuracy <- pm_subset_accuracy %>%
  group_by(id,list) %>%
  summarise(mean_acc = mean(correct)) %>% 
  arrange(mean_acc)
participant_accuracy #participant by list
```

## rt calc
separate by language
import and merge sign_start data into individual language dfs
calculate actual rt by language

```{r, warning = F, message=F}
#separate by language
data_factors <- pm_subset_accuracy %>%  mutate_if(is.character, as.factor)
data_factors$language <- data_factors$list 
head(data_factors)
str(data_factors)
data_factors <- data_factors %>% mutate(language = recode(language, 
                          nsl_list1 = "nsl",
                          nsl_list2 = "nsl",
                          rsl_list1 = "rsl",
                          rsl_list2 = "rsl"))
data_factors
data_factors$raw_rt <- as.numeric(as.character(data_factors$raw_rt)) #convert to numeric (double returned wack values)

nsl_subset <- subset(data_factors, language == "nsl") %>% droplevels()
rsl_subset <- subset(data_factors, language == "rsl") %>% droplevels()
str(nsl_subset)
str(rsl_subset)
```

### import and merge sign_start data into main df
the time in the video where the signer begins to produce the sign. this must be subtracted from the raw rt to arrive at the actual rt
```{r, warning = F, message=F}
# import and merge sign_start data into individual language dfs
signstart_import <- read_excel("DEPICT WP1 stimuli list.xlsx", sheet = "masterlist")

#nsl
nsl_signstart <- select(signstart_import, c("item","NSL_sign_start"))
head(nsl_signstart)

#rsl
rsl_signstart <- select(signstart_import, c("item","RSL_sign_start"))
head(rsl_signstart)
signstart <- merge(nsl_signstart,rsl_signstart, by = "item")
head(signstart)
prertcalc_df <- merge(data_factors, signstart, by = "item")
head(prertcalc_df)
```

### calculate actual rt by language
```{r}
rtcalc_df <- prertcalc_df %>%
  mutate(rt = case_when(
    language == "rsl" ~ raw_rt - RSL_sign_start,
    language == "nsl" ~ raw_rt - NSL_sign_start,
    TRUE ~ NA_real_  # Handles other cases (if any)
))
```

# redo condition values
Randomization in Gorilla caused the column "condition" to incorrectly align with responses.

## nsl lists
Recreate from picture id such that for:
nsl lists all pic_id ending in 1 = aligned, ending in 2 = misaligned

```{r}
#redo lang subsetting
nsl_subset2 <- subset(rtcalc_df, language == "nsl") %>% droplevels()

#create new column with pic_id ending in 1 = aligned, 2 = misaligned using stringr:separate()

head(nsl_subset2)
str(nsl_subset2)
nsl_subset_recode_prep <- nsl_subset2 %>% separate(pic_id, c("item_id", "pic_num"), sep = " ") %>% #split at the space
  mutate_if(is.character,as.factor)%>%  #convert strings to factors again 
  separate(pic_num, into = c("pic_num", "jpg"), sep = "\\.") %>% #split at period but don't include the period
  mutate_if(is.character,as.factor) %>% 
  select(-jpg) #select cols
head(nsl_subset_recode_prep)
str(nsl_subset_recode_prep)

nsl_subset_recoded <- nsl_subset_recode_prep %>%
  mutate(condition = if_else(pic_num == "1", "aligned", "nonaligned")) %>%  #recode pic 1 as aligned
  mutate_if(is.character,as.factor)
head(nsl_subset_recoded)
str(nsl_subset_recoded)
```

##rsl_lists
rsl lists all pic_id ending in 2 = aligned, ending in 1 = misaligned (except for the cognates. for these 1 = aligned, 2 = misaligned). hence:

noncognate list: "Cabbage", "Engagement", "Color", "Doll", "East", "Frog", "Gorilla", "Magazine", "Ring", "Salt", "School", "Pain", "Call", "Come", "Doubt", "Play", "Choose", "Sail", "Show", "Sneeze", "Travel", "Try", "Wait", "Win"

cognate list: "Beauty", "Book", "Boy", "Children", "Coffee", "Cigar", "Eagle", "Family", "Flower", "Change", "Metal", "Telephone", "Breathe", "Cry", "Jump", "Leave", "Lose", "Paint", "Run", "Sing", "Take", "Think", "Watch"


```{r}
#redo language subsetting
rsl_subset2 <- subset(rtcalc_df, language == "rsl") %>% droplevels()

##create new column with pic_id ending in 1 = aligned, 2 = misaligned using stringr:separate()
head(rsl_subset2)
str(rsl_subset2)
rsl_subset_recode_prep <- rsl_subset2 %>% separate(pic_id, c("item_id", "pic_num"), sep = " ") %>% #split at the space
  mutate_if(is.character,as.factor) %>% #convert strings to factors again
  separate(pic_num, into = c("pic_num", "jpg"), sep = "\\.") %>%  #split at period, but don't include the period
  mutate_if(is.character,as.factor) %>% 
  select(-jpg) #drop extra column
head(rsl_subset_recode_prep)
str(rsl_subset_recode_prep)

# recode noncognates
rsl_subset_noncognates <- rsl_subset_recode_prep %>% 
  filter(item_id %in% c("Cabbage", "Engagement", "Color", "Doll", "East", "Frog", "Gorilla", "Magazine", "Ring", "Salt", "School", "Pain", "Call", "Come", "Doubt", "Play", "Choose", "Sail", "Show", "Sneeze", "Travel", "Try", "Wait", "Win")) %>% 
  droplevels()
head(rsl_subset_noncognates)
levels(rsl_subset_noncognates$item)
rsl_subset_noncognates_recoded <- rsl_subset_noncognates%>% 
  mutate(condition = if_else(pic_num == "2", "aligned", "nonaligned")) %>% #recode pic 2 as aligned
  mutate_if(is.character,as.factor)
head(rsl_subset_noncognates_recoded)
str(rsl_subset_noncognates_recoded)

# recode cognates
rsl_subset_cognates <- rsl_subset_recode_prep %>% 
  filter(item_id %in% c("Beauty", "Book", "Boy", "Children", "Coffee", "Cigar", "Eagle", "Family", "Flower", "Change", "Metal", "Telephone", "Breathe", "Cry", "Jump", "Leave", "Lose", "Paint", "Run", "Sing", "Take", "Think", "Watch", "Write")) %>% 
  droplevels()
head(rsl_subset_cognates)
levels(rsl_subset_cognates$item_id)
rsl_subset_cognates_recoded <- rsl_subset_cognates %>% 
  mutate(condition  = if_else(pic_num == "1", "aligned", "nonaligned")) %>% #recode pic 1 as aligned
  mutate_if(is.character,as.factor)
head(rsl_subset_cognates_recoded)
str(rsl_subset_cognates_recoded)

# rbind both frame back together
rsl_subset_recoded <- rbind(rsl_subset_cognates_recoded, rsl_subset_noncognates_recoded) 

```

## recombine recoded condition dfs

```{r}
pm_data <- rbind(nsl_subset_recoded,rsl_subset_recoded)  %>% mutate_if(is.character,as.factor)
head(pm_data)
str(pm_data)
```

## check that the error is fixed
```{r}
# Filtered by 1 nsl participant 9462565 (list1)
# checked that cabbage 1 (noncognate) is now coded as "aligned" (was incorrectly labeled "different" in gorilla export)
# checked that gorilla 2 (noncognate) is now coded as "misaligned" (was correctly labeled "different" in the gorilla export)
# 
# checked that beauty 1 (cognate) is now coded as "aligned" (was incorrectly labeled "different" in the gorilla export)
# checked that eagle 2 (cognate) is now coded as "misaligned" (was correctly labeled "different" in the gorilla export)
# 
# Filtered by 1 rsl participant 9377336 (list2)
# checked that cabbage 1 (noncognate) coded as "misaligned" (was correctly labeled "different" in the gorilla export)
# checked that gorilla 2 (noncognate) coded as "aligned" (was correctly labeled "same" in the gorilla export)
# 
# checked that beauty 1 (cognate) is now coded as "aligned" (was incorrecly labeled "different" in the gorilla export)
# checked that eagle 2 (cognate) is now coded as "misaligned" (was correctly labeled "different" in the gorilla export)
str(pm_data)
pm_data_filtered <- pm_data %>%
  filter(id %in% c(9462565, 9377336),
         item %in% c("cabbage", "gorilla", "beauty", "eagle"),
         pic_num %in% c(1,2),
         condition %in% c("aligned", "misaligned"),
         oops %in% c("same","different")) %>% 
  select(id, list, item, trial, pic_num,oops, condition, rt) %>% 
  mutate(cognate = ifelse(item %in% c("beauty", "cabbage"), "cognate", "noncognate")) %>% 
  arrange(cognate, pic_num)
pm_data_filtered

check_filter <-
  pm_data_filtered %>%
  group_by(condition,cognate,oops) %>%
  summarise(average = mean(rt)) %>%
  arrange(condition, desc(average))
check_filter
```

## create cognate column
```{r}
cognates <- c("Beauty", "Book", "Boy", "Children", "Coffee", "Cigar", "Eagle", "Family", "Flower", "Change", "Metal", "Telephone", "Breathe", "Cry", "Jump", "Leave", "Lose", "Paint", "Run", "Sing", "Take", "Think", "Watch", "Write")
noncognates <- c("Cabbage", "Engagement", "Color", "Doll", "East", "Frog", "Gorilla", "Magazine", "Ring", "Salt", "School", "Pain", "Call", "Come", "Doubt", "Play", "Choose", "Sail", "Show", "Sneeze", "Travel", "Try", "Wait", "Win")

pm_data_conds <- pm_data %>%
  mutate(cognate = case_when(
    .$item_id %in% cognates ~ "cognate",
    .$item_id %in% noncognates ~ "noncognate",
    TRUE ~ "other"
  ))
head(pm_data_conds)
```



## select only needed vectors
```{r}
experiment_df <- pm_data_conds %>% select(id, list, item, trial, language, condition, cognate, correct, rt)
head(experiment_df)
```

# itemvars_df
## import wordclass, frequency, and homophone status  
```{r, warning = F, message=F}
itemsvars_import <- read_excel("DEPICT WP1 stimuli list.xlsx", sheet = "masterlist")

# wordclass, homophone, boundedness, plurality
itemvars <- select(itemsvars_import, c("item","wordclass", "homophone", "boundedness","plurality"))
head(itemvars)
itemvars_df <- itemvars
  # select(-language,-list,-id,-trial,-condition,-correct, -rt)
```

## frequency
n.b. before pushing to osf uncouple experiment_df from itemvars_df
```{r}
#nsl
nsl_freq <- select(itemsvars_import, c("item","nsl_log", "norsk_log")) #%>%
head(nsl_freq)

#rsl
rsl_freq <- select(itemsvars_import, c("item","rsl_log","rusisk_log")) #%>%
head(rsl_freq)

# #merge nsl, rsl freq
freq <- merge(nsl_freq,rsl_freq, by = "item")
head(freq)
str(freq)

freq_df0 <- merge(experiment_df, freq, by = "item") #this is where you should uncouple
head(freq_df0)
 
# merge columns nsl and rsl log into "freq"
freq_df1<- freq_df0 %>%
   mutate(freq = ifelse(language == "nsl", nsl_log, rsl_log))%>%
   select(-c(nsl_log, rsl_log))
head(freq_df1)

#bin freq into high and low
freq_df <- freq_df1 %>%
  mutate(median_freq = median(freq),
         freq_bin = ifelse(freq > median_freq, 'high', 'low')) %>%
  select(-c(median_freq))
head(freq_df)

#remerge into itemvars_df
itemsvars_df1 <- merge(freq_df, itemvars_df, by = "item")
head(itemsvars_df1)

itemvars_df <- itemsvars_df1
rm(itemsvars_df1, freq_df, freq_df0, freq_df1)
```

#survey_df
## load survey data 
```{r, echo=T, message=FALSE, warning=FALSE}
survey_import <-
    list.files(pattern = "qcg3|1v1w", recursive = T) %>% #search all files in all directories contain the string in pattern
    map_df(~read_csv(., col_types = cols(.default = "c"))) #return data frames by row- or column-binding the outputs together.
```

## choose columns
```{r}
survey1 <- select(survey_import, c("Participant Private ID", "Tree Node Key","Response Type","Response","Object Name", "Spreadsheet: item"))
head(survey1)
survey2 <- survey1  %>% rename("id" = "Participant Private ID", #participant
                           "window" = "Response Type", #all gorilla windows with variables of interest
                           "question"= "Object Name", # question type (Familiarity,Use, Similarity)
                           "item" = "Spreadsheet: item", #item
                           "rating" = "Response", #question response
                           "language" = "Tree Node Key") #participant group
head(survey2)
survey3 <- subset(survey2, window %in% c("response")) #only responses to items
head(survey3)
survey4 <- survey3 %>% mutate(language = recode(language,
                          'task-qcg3' = "nsl",
                          'task-1v1w' = "rsl"))
survey_spread <- survey4 %>% spread(key = question, value = rating) %>% 
  rename(Iconicity = Similarity)
head(survey_spread)
rm(survey_import, survey1, survey2, survey3, survey4)

```

## bin use, familiarity, and iconicity
```{r}
#convert strings to numbers
survey_spread$Familiarity <- as.numeric(as.character(survey_spread$Familiarity))
survey_spread$Iconicity <- as.numeric(as.character(survey_spread$Iconicity))

# summarize condition means by item and language

survey_item_means <-
  survey_spread %>%
  group_by(item,language,id) %>%
  reframe(
    Use = mean(Use == "yes"),
    Familiarity = mean(Familiarity),
    Iconicity = mean(Iconicity)
    ) %>%
  arrange(item)
survey_item_means

nsl_survey_item_means <- subset(survey_item_means, language == "nsl")
rsl_survey_item_means <- subset(survey_item_means, language == "rsl")
```

### nsl
nsl bin for use, familiarity, and iconicity
```{r}
## get means
nsl_use_mean <- mean(nsl_survey_item_means$Use, na.rm = TRUE)
nsl_iconicity_mean <- mean(nsl_survey_item_means$Iconicity, na.rm = TRUE)
nsl_familiarity_mean <- mean(nsl_survey_item_means$Familiarity, na.rm = TRUE)
nsl_freq_mean <- mean(freq$nsl_log, na.rm = TRUE)

## bin
nsl_survey_item_means$use_bin <- ifelse(nsl_survey_item_means$Use > nsl_use_mean, "high", "low")
nsl_survey_item_means$icon_bin <- ifelse(nsl_survey_item_means$Iconicity > nsl_iconicity_mean, "high", "low")
nsl_survey_item_means$fam_bin <- ifelse(nsl_survey_item_means$Familiarity > nsl_familiarity_mean, "high", "low")
# View(nsl_survey_item_means)
# rm(nsl_use_mean, nsl_iconicity_mean, nsl_familiarity_mean)
```

### rsl
rsl bin for use, familiarity, and iconicity
```{r}
## get means
rsl_use_mean <- mean(rsl_survey_item_means$Use, na.rm = TRUE)
rsl_iconicity_mean <- mean(rsl_survey_item_means$Iconicity, na.rm = TRUE)
rsl_familiarity_mean <- mean(rsl_survey_item_means$Familiarity, na.rm = TRUE)

## bin
rsl_survey_item_means$use_bin <- ifelse(rsl_survey_item_means$Use > rsl_use_mean, "high", "low")
rsl_survey_item_means$icon_bin <- ifelse(rsl_survey_item_means$Iconicity > rsl_iconicity_mean, "high", "low")
rsl_survey_item_means$fam_bin <- ifelse(rsl_survey_item_means$Familiarity > rsl_familiarity_mean, "high", "low")
rsl_survey_item_means
# rm(rsl_use_mean, rsl_iconicity_mean, rsl_familiarity_mean)
```

### recombine and select cols
```{r}
# rbind nsl and rsl bins
survey_item_means_bin <- rbind(nsl_survey_item_means, rsl_survey_item_means) %>%
  select(item, language, id, use_bin, icon_bin, fam_bin)
survey_item_means_bin

# merge back into full survey with by-participant values
head(survey_spread)
head(survey_item_means_bin)

survey_bin <- left_join(survey_spread, survey_item_means_bin, by = c("item"="item","language"="language","id"="id")) %>% select(-window)
head(survey_bin)
# rm(survey_item_means_bin)
str(survey_bin)
survey_df <- select(survey_bin, c("id","item","language", "Familiarity", "Iconicity", "Use", "fam_bin","icon_bin","use_bin"))# only needed columns 
head(survey_df)
# View(survey_df)
```


# load language background data (quest)
load and merge lg bg data
  1_dob-year
  4_handedness-quantised (1 = right, left = 2, both = 3)
  5_hearinglevel-quantised (1 = serious,2 = considerable, 3 = moderate, 4 = mild)
  6_hearing-aids-quantised (1 = yes, 2 = no)
  6a_CI-quantised (1 = yes, 2 = no)
  8_born-deaf-quantised (yes = 1, 2 = no)
  9_SL-exposure (free answer)
  10_SL-introduction-path-quantised (1 = parents, 2 = siblings, 3 = caregiver, 4 = school, 5 = annet)
  12_SL-peers-quantised (yes = 1, 2 = no)
  13_college-quantised (yes = 1, 2 = no)
  15_freq-of-use-quantised (1= everyday, 2 = several times a week, 3 = once a week, 4= within a month, 5 = very rarely, 6 = never)
  16_preferred-language-quantised (1 = sign language, 2 = written norwegian/russian, 3 = spoken norwegian/russian, 4 = both, 5 = other)

```{r}
quest_wide <- list.files(pattern = "zt1x|3kt6", recursive = T) %>% #search all files in all directories contain the string in pattern
    map_df(~read_csv(., col_types = cols(.default = "c"))) #return data frames by row- or column-binding the outputs together.
#zt1x = nsl
#3kt6 = rsl

head(quest_wide)
```

## select columns from full survey
```{r}
quest_select <- quest_wide %>%
  select("Participant Private ID", "Question Key", "Response") %>% 
  rename(
    "id"= "Participant Private ID",
    "question" = "Question Key",
    "response" = "Response") %>%
  filter(question %in% 
           c("1_dob-year",
             "4_handedness-quantised",
             "5_hearinglevel-quantised",
             "8_born-deaf-quantised",
             "9_SL-exposure",
             "10_SL-introduction-path-quantised",
             "12_SL-peers-quantised",
             "15_freq-of-use-quantised"))
str(quest_select)
```

## rename values

```{r}
# rename values
quest_wide_renamed <- quest_select %>%
  mutate(response = case_when(
    question == "4_handedness-quantised" & response == 1 ~ "right",
    question == "4_handedness-quantised" & response == 2 ~ "left",
    question == "4_handedness-quantised" & response == 3 ~ "both",
    
    question == "5_hearinglevel-quantised" & response == 1 ~ "serious",
    question == "5_hearinglevel-quantised" & response == 2 ~ "considerable",
    question == "5_hearinglevel-quantised" & response == 3 ~ "moderate",
    question == "5_hearinglevel-quantised" & response == 4 ~ "mild",
    
    question == "8_born-deaf-quantised" & response == 1 ~ "yes",
    question == "8_born-deaf-quantised" & response == 2 ~ "no",
    
    question == "10_SL-introduction-path-quantised" & response == 1 ~ "parents",
    question == "10_SL-introduction-path-quantised" & response == 2 ~ "siblings",
    question == "10_SL-introduction-path-quantised" & response == 3 ~ "caregiver",
    question == "10_SL-introduction-path-quantised" & response == 4 ~ "school",
    question == "10_SL-introduction-path-quantised" & response == 5 ~ "other",
    
    question == "12_SL-peers-quantised" & response == 1 ~ "yes",
    question == "12_SL-peers-quantised" & response == 2 ~ "no",
    
    question == "15_freq-of-use-quantised" & response == 1 ~ "daily",
    question == "15_freq-of-use-quantised" & response == 2 ~ "often",
    question == "15_freq-of-use-quantised" & response == 3 ~ "weekly",
    question == "15_freq-of-use-quantised" & response == 4 ~ "monthly",
    question == "15_freq-of-use-quantised" & response == 5 ~ "rarely",
    question == "15_freq-of-use-quantised" & response == 6 ~ "never",
  TRUE ~ as.character(response)
  )  )
head(quest_wide_renamed)

```

## spread 
such that question is in separate columns
```{r}
quest_spread <- quest_wide_renamed %>%
  group_by(id, question) %>%
  summarise(response = first(response)) %>% # first group,
  spread(key = question, value = response) %>% # then spread,
  rename( #then rename
    age = "1_dob-year",
    handedness = "4_handedness-quantised", 
    hearing = "5_hearinglevel-quantised",
    deafbirth = "8_born-deaf-quantised",
    exposure = "9_SL-exposure",
    learned =  "10_SL-introduction-path-quantised",
    peers = "12_SL-peers-quantised",
    practice ="15_freq-of-use-quantised"
    ) %>% 
  mutate(age = 2023 - as.numeric(age)) #then calc age
quest_df <- quest_spread
# View(quest_df)
```

## merge with survey
```{r}
survey_quest_df <- left_join(survey_df, quest_df, by = c("id"="id"))
head(survey_quest_df)
# write.csv(survey_quest_df, "quest_check.csv")

```


# merge everything
experiment_df, survey_df, quest_df, itemvars_df
note that experiment_df is already in itemvars_df pga frequency bin
survey and quest dfs are already merged in survey_quest_df
```{r}
head(experiment_df)
head(itemvars_df)
head(survey_df)
head(quest_df)

merged_df <- left_join(itemvars_df, survey_quest_df, by = c("id"="id","item"="item","language"="language"))
head(merged_df)
```


# export to csv
```{r}
write.csv(merged_df, "pm_osf_dataframe_with_survey_quest.csv")
```




